---
title: "Ignorant Causes"
author: "Lara Kirfel & David Lagnado"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")
```

# Install packages

```{r, message=FALSE}
install.packages("pastecs");
install.packages("reshape")
install.packages("lubridate")
install.packages("lsr")
install.packages("janitor")
install.packages("DT")
install.packages("Hmisc")
install.packages("broom")
install.packages("tidyverse")
install.packages("ez")
install.packages("schoRsch")
install.packages("stringr")
install.packages('Rdpack')
install.packages("afex")
install.packages("VGAM")
install.packages("mlogit", repo = 'https://mac.R-project.org')
install.packages("car")
install.packages("emmeans")

```

# Load packages 

```{r, message=FALSE}
library("pastecs")
library("reshape")
library("knitr")
library("lubridate")
library("lsr")
library("janitor") # for cleaning variable names 
library("DT") # for nice tables
library("Hmisc") # for smean function for bootstrapped confidence intervals 
library("broom") # for tidy regression results
library("tidyverse") # for data wrangling, visualization, etc. 
library("ez")
library("schoRsch")
library("lme4")
library("stringr")
library("dplyr")
library("nlme")
library("afex")
library("mlogit")
library("car")
library("emmeans")


```

```{r}
# set ggplot theme 
theme_set(
  theme_classic()
)
```

# Experiment 1:

## Read in Data

```{r}
df.data = read.csv(file = "EpStates_1.csv", stringsAsFactors = F, sep = ",") %>% 
  filter(row_number() > 2) %>% # additional rows in qualtrics csv
  clean_names() %>% 
  filter(distribution_channel != "preview",
         !condition =="", #exclude bot fails,
          progress ==100| progress==99|progress==98)
 
```

## Structure and edit data

```{r}

df.exp = df.data %>% 
  mutate(participant = 1:n()) %>% 
  rename(duration=duration_in_seconds) %>% 
  mutate(duration=as.numeric(duration)) %>% 
  select(h_check_fact_1:b_cf_2,
         participant,
         order,
         duration,
         condition,
         gender,
         age,
         -starts_with("q")
         ) %>% 
  gather("index", "value", -c(participant, condition, duration, order))%>% 
  filter(value != "") %>%
  arrange(index)%>%
  mutate(index = ifelse(str_detect(index,"_c_1"),
                        "cause_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_c_2"),
                        "cause_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_cf_1"),
                        "cf_no_knowledge",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_cf_2"),
                        "cf_knowledge",
                        index)) %>% 
  mutate(index = ifelse(str_detect(index,"fact_1"),
                        "fact_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"fact_2"),
                        "fact_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"know_1"),
                        "know_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"know_2"),
                        "know_2",
                        index)) %>% 
  mutate(order = ifelse(order == 1,"dont know first", 
                          ifelse(order == 2, "know first", " ")))%>%
  mutate(scenario = ifelse(condition == 1,"Hospital", 
                          ifelse(condition == 2, "Garden", 
                          ifelse(condition == 3, "Bakery", " "))))%>%
  spread(index, value) %>%
  arrange(participant)

```

## Create and set participant filter

```{r}
####Experiment 1: Create filter
df.exp<- df.exp%>%  
  mutate(check_total=if_else(know_1=="2", 1, 0)) %>% 
  mutate(check_total=if_else(know_2 =="1", check_total+1, check_total)) %>% 
  mutate(check_total=if_else(fact_1 =="1", check_total+1, check_total)) %>% 
  mutate(check_total=if_else(fact_2=="1",  check_total+1, check_total)) 
           
#### Apply filter
df.exp<-df.exp %>% 
  filter(check_total ==4) ####Set to 4 to change exlusion criterion to "all check questions correct"
```


##### Export Counterfactual Responses for separate analysis (see analysed datasheet ``Counterfactuals_analysed'' in folder)

#```{r}

df.exp_cf = df.exp %>% 
  select(participant,
         condition,
         contains("cf"))%>% 
  gather("index", "value", -c(participant, condition))%>% 
  filter(value != "") %>%
  arrange(index)%>%
  mutate(index = ifelse(str_detect(index,"cf_1"),
                        "not_know",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"cf_2"),
                        "know",
                        index))%>% 
  mutate(scenario = ifelse(condition == 1,"hospital", 
                          ifelse(condition == 2, "garden", 
                          ifelse(condition == 3, "bakery", " "))))%>%
  spread(index, value) %>%
  arrange(participant)

write.csv(df.exp_cf,'Counterfactuals.csv')
#```



##Join dataframe with Analysed Counterfactual Responses Dataframe

```{r}
df.counterfactuals<-read.csv("Counterfactuals_analysed.csv") %>% 
  select(participant, code_1, detailed_1, code_2, detailed_2) 
  
df.exp<-df.exp %>% 
inner_join(df.counterfactuals, by="participant") %>% 
filter(code_1 != "0")
```

### Demographics
```{r}
####Experiment 1
###Demographics

df.exp_demo <- df.exp %>% 
  select(age, gender, duration) %>% 
  mutate(age=as.numeric(age)) %>%
  transform(gender= ifelse(gender==1, "Male", #recode numbers into gender categories
                    ifelse(gender==2, "Female",
                    ifelse(gender==3, "Prefer not to say", gender)))) %>% 
  filter(age<100 |age ==" ") %>% #remove outliers (year) or N.A.s
  summarize(n=n(),
             female=sum(gender=="Female"),
             not_say=sum(gender=="Prefer not to say"),
             mean_age = mean(age),
             std_age=sd(age),
             mean_time=mean(duration/60),
             sd_time=sd(duration/60)
            )
```

## Create dataframe in long format

```{r}
####### Createlong Dataframe


df.exp_long = df.exp %>% 
  select(scenario,
         order,
         participant,
         contains("cause"),
         contains("code"),
         contains("detailed"))%>%
  gather(condition, rating, "cause_1":"detailed_2") %>%  
  mutate(knowledge = ifelse(str_detect(condition, "1"),
                        "Ignorance", "Knowledge")) %>% 
  mutate(condition = ifelse(str_detect(condition, "cause"),"causal_rating", 
                                ifelse(str_detect(condition, "code"), "counterfactual", 
                                       "counterfactual_specific"))) %>% 
  spread(condition, rating) %>% 
  mutate(scenario=as.factor(scenario)) %>% 
  mutate(knowledge=as.factor(knowledge)) %>% 
  mutate(knowledge= ordered(knowledge, levels = c("Knowledge", "Ignorance"))) %>% 
  mutate(causal_rating=as.numeric(causal_rating)) %>% 
  mutate(counterfactual=dplyr::recode(counterfactual, 
                               "1" ="action",
                               "2" ="epistemic state",
                               "3" = "agent-related", 
                               "4" = "environment")) %>% 
  mutate(counterfactual=factor(counterfactual, levels=c("action", "epistemic state", "agent-related", "environment")))

```


##### Create Graph for Causal and Counterfactual responses

```{r}

### Set GGplot Theme
myTheme <-   theme(axis.title.x  = element_blank(), 
                   axis.title.y = element_text(color="black", size = 14, vjust=.9), 
                   axis.text.x = element_text(color="black", size = 14),
                   axis.text.y = element_text(color="black", size = 14), 
                   strip.text.x = element_text(color="black", size = 14),
                   legend.text = element_text(color="black", size = 14),
                   legend.position = "top",
                   legend.title = element_blank(),
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))
    

################# Causal Responses

CausalExp1 <- ggplot(df.exp_long, aes(x=knowledge,y=causal_rating, fill = knowledge, colour = knowledge))+
  coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(0, 7, by=1))+
  geom_line(aes(group=participant),position = position_jitter(width = .1), size = 1, alpha=0.1)+ #Create lines between points for each subject
  stat_summary(fun=mean, geom='line',color='black',  group = 1, position = position_nudge(x=.1))+ #Create grand averaged effects line
  #geom_flat_violin(position = position_nudge(x = .1, y = 0),adjust =1.5, alpha=0.5)+
  geom_point(position = position_jitter(width = .1), size = 1, alpha=0.5)+
  stat_summary(fun.data = mean_cl_normal, geom = "pointrange", position = position_nudge(x=.1), colour = "BLACK", width = 0.5,
  size = 1.2, shape = 21, fatten = 2.5)+
  scale_fill_manual(values=c("#999999", "#E69F00"), name="blank", labels=c("Knowledge", "Ignorance"))+
  scale_colour_manual(values=c("#999999", "#E69F00"), name="blank", labels=c("Knowledge", "Ignorance"))+
  labs( y="Causal Rating")+
  theme_bw()+
  guides(fill = FALSE, colour = FALSE) +
  facet_grid(~scenario)+
  myTheme

  
CausalExp1
### Export Figure
ggsave(CausalExp1, file="Fig1a.pdf", dpi=400, height = 5, width = 8)

##################### Counterfactual Responses

CFExp1<-ggplot(df.exp_long, aes(x=counterfactual, group=knowledge))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  coord_cartesian(ylim = c(0,1)) +
  scale_y_continuous(labels=scales::percent_format(accuracy = 1), breaks = seq(0, 1, by=0.20)) +
  ylab("proportion of responses") +
  facet_wrap(~knowledge)+
  scale_fill_brewer(palette="Greys", direction=-1)+
  theme_bw()+
  myTheme+
  theme(legend.position= "none")+
  theme(
    axis.text.x = element_text(angle = 20, hjust = 1, color="black", size = 14))

CFExp1
###Expot Figure
ggsave(CFExp1, file="Fig1b.pdf", dpi=400, height = 5, width = 8)

```


######create new Dataframe for Between Subject Analysis

```{r}
####Create Dataframe for between subjects analysis
df.exp_long2 <- df.exp_long %>% 
  filter(order == "know first" & knowledge == "Knowledge" |order == "dont know first" & knowledge == "Ignorance") 
  
```

### Experiment 1
### Test Fixed Effects: Causal Ratings

```{r}

################### Within Contrasts

#df.exp_long <- within(df.exp_long, knowledge <- relevel(knowledge, ref = 'Knowledge'))
#df.exp_long <- within(df.exp_long, scenario<- relevel(scenario, ref = 'bakery'))


mixed(causal_rating ~ 1 + knowledge*scenario +  (1 | participant), df.exp_long, method = 'LRT')
C1  <- lmer(causal_rating ~ 1 + knowledge*scenario + (1 | participant), df.exp_long, REML=T)
summary(C1)

C1_posthoc <- emmeans(C1, pairwise ~ knowledge)
summary(C1_posthoc)

################### Between Contrasts

C1b  <- lm(causal_rating ~ 1 + knowledge*scenario , df.exp_long2)
C1b %>% Anova()

####post hoc tests
C1b_posthoc <- emmeans(C1b, pairwise ~ knowledge|scenario)
summary(C1b_posthoc)
```


###### Descriptives Causal Jugdments,  Within Contrast

```{r}

#### Descriptives, Within Contrast

df.exp_desc_causal<- df.exp_long%>%
  group_by(knowledge) %>%
  summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96
)

```

###### Descripives Causal Judgments, Between Contrast

```{r}
#### Descriptives, Between Contrast

df.exp_desc_causal2<- df.exp_long2%>%
  group_by(knowledge, scenario) %>%
  summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96
)

```

###### Create Dataframe and Descriptives of Counterfactual Responses, Within Contrast

```{r}

#### Dataframe, Within Contrast

df.exp_cf<- df.exp_long %>% 
  select(participant, scenario, order, knowledge, counterfactual)

#### Descriptives, Within Contrast

df.exp_cf_desc <- df.exp_cf%>% 
  select(scenario, counterfactual, knowledge) %>% 
  group_by(counterfactual, knowledge) %>% 
  summarize(n=n()) %>% 
  ungroup(counterfactual) %>% 
  mutate(total=sum(n)/2,
         freq=n/total)

```

###### Create Dataframe and Descriptives of Counterfactual Responses, Between Contrast

```{r}

#### Dataframe, Between Contrast

df.exp_cf2<- df.exp_cf%>% 
  filter(order == "know first" & knowledge == "Knowledge" |order == "dont know first" & knowledge == "Ignorance") 

#### Descriptives, Between Contrast

df.exp_cf_desc2 <- df.exp_cf2%>% 
  select(scenario, counterfactual, knowledge) %>% 
  group_by(counterfactual, knowledge) %>% 
  summarize(n=n()) %>% 
  ungroup(counterfactual) %>% 
  group_by(knowledge) %>% 
  mutate(total=sum(n),
         freq=n/total)

```

###### Counterfactual Response Analysis:  Within Contrasts
```{r}

library(VGAM)
vglm1 <- vglm(counterfactual ~ knowledge, family=multinomial(refLevel="environment"), df.exp_cf) #full model
vglm0 <- vglm(counterfactual ~ +1, family=multinomial(refLevel="environment"), df.exp_cf) #null model

# Descriptives
colSums(depvar(vglm1))

## LR Test
VGAM::lrtest(vglm0, vglm1)
summary(vglm1)


####Odds ratios
exp(coef(vglm1))

####R-Squared
LLf   <- logLik(vglm1)
LL0   <- logLik(vglm0)
as.vector(1 - (LLf / LL0))

```

###### Counterfactual Response Analysis:  BetweenContrasts
```{r}

library(VGAM)
vglm1 <- vglm(counterfactual ~ knowledge, family=multinomial(refLevel="environment"), df.exp_cf2)
vglm0 <- vglm(counterfactual ~ +1, family=multinomial(refLevel="environment"), df.exp_cf2)

# Descriptives
colSums(depvar(vglm1))

## LR Test
VGAM::lrtest(vglm0, vglm1)
summary(vglm1)


####Odds ratios
exp(coef(vglm1))

####R-Squared
LLf   <- logLik(vglm1)
LL0   <- logLik(vglm0)
as.vector(1 - (LLf / LL0))
```








