---
author: "Lara Kirfel & David Lagnado"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")
```

# Install packages

```{r, message=FALSE}
install.packages("pastecs");
install.packages("reshape")
install.packages("lubridate")
install.packages("lsr")
install.packages("janitor")
install.packages("DT")
install.packages("Hmisc")
install.packages("broom")
install.packages("tidyverse")
install.packages("ez")
install.packages("schoRsch")
install.packages("stringr")
```

# Load packages 

```{r, message=FALSE}
library("pastecs")
library("reshape")
library("knitr")
library("lubridate")
library("lsr")
library("janitor") # for cleaning variable names 
library("DT") # for nice tables
library("Hmisc") # for smean function for bootstrapped confidence intervals 
library("broom") # for tidy regression results
library("tidyverse") # for data wrangling, visualization, etc. 
library("ez")
library("schoRsch")
library("lme4")
library("stringr")
library("dplyr")
library("nlme")

```

```{r}
# set ggplot theme 
theme_set(
  theme_classic()
)
```

# Experiment 4:

## Read in Data

```{r}
df.data = read.csv(file = "EpStates_4_noInfo.csv", stringsAsFactors = F, sep = ",") %>% 
  filter(row_number() > 2) %>% # additional rows in qualtrics csv
  clean_names() %>% 
  filter(distribution_channel != "preview",
         !condition =="", #exclude bot fails,
          progress ==100| progress==99|progress==98)
 
```

## Structure and edit data

```{r}

df.exp = df.data %>% 
  mutate(participant = 1:n()) %>% 
  rename(duration=duration_in_seconds) %>% 
  mutate(duration=as.numeric(duration)) %>% 
  select(h_check_fact_1:b_outcome_a1_4,
         participant,
         order,
         duration,
         condition,
         gender,
         age,
         -starts_with("q")
         ) %>% 
  gather("index", "value", -c(age, gender, participant, condition, duration, order))%>% 
  filter(value != "") %>%
  arrange(index)%>%
  mutate(index = ifelse(str_detect(index,"_c_1"),
                        "cause_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_c_2"),
                        "cause_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_cf_1"),
                        "cf_externally_caused",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_cf_2"),
                        "cf_self_caused",
                        index)) %>% 
  mutate(index = ifelse(str_detect(index,"_k_1"),
                        "could_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_k_2"),
                        "could_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_b_1"),
                        "blame_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_b_2"),
                        "blame_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_look_a1"),
                        "look_a1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_look_a2"),
                        "look_a2",
                        index)) %>% 
  mutate(index = ifelse(str_detect(index,"_outcome_a1_"),
                        "outcome_a1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_outcome_a2_"),
                        "outcome_a2",
                        index))%>%
  mutate(index = ifelse(str_detect(index,"fact_1"),
                        "fact_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"fact_2"),
                        "fact_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"know_1"),
                        "know_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"know_2"),
                        "know_2",
                        index)) %>% 
  mutate(index = ifelse(str_detect(index,"mail_1"),
                        "mail_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"mail_2"),
                        "mail_2",
                        index)) %>%
  mutate(index = ifelse(str_detect(index,"read_1"),
                        "read_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"read_2"),
                        "read_2",
                        index)) %>%
  mutate(order = ifelse(order == 1,"reads e-mail first", 
                          ifelse(order == 2, "doesn't read e-mail first", " ")))%>%
  mutate(scenario = ifelse(condition == 1,"hospital", 
                          ifelse(condition == 2, "garden", 
                          ifelse(condition == 3, "bakery", " "))))%>%
  spread(index, value) %>%
  arrange(participant)

```

#### Create Filter

```{r}
####Experiment 4: Create filter
df.exp<- df.exp%>%  
  mutate(check_total=if_else(know_1=="2", 1, 0)) %>% 
  mutate(check_total=if_else(know_2 =="2", check_total+1, check_total)) %>% 
  mutate(check_total=if_else(fact_1 =="1", check_total+1, check_total)) %>% 
  mutate(check_total=if_else(fact_2=="1",  check_total+1, check_total)) %>% 
  mutate(check_total=if_else(read_1=="1",  check_total+1, check_total)) %>% 
  mutate(check_total=if_else(read_2=="2",  check_total+1, check_total)) %>% 
  mutate(check_total=if_else(mail_1=="1",  check_total+1, check_total)) %>% 
  mutate(check_total=if_else(mail_2=="1",  check_total+1, check_total))


#### Set filter
df.exp<-df.exp %>% 
  filter(check_total ==8)
```


##### Export Counterfactual Responses for separate analysis (see analysed datasheet ``Counterfactuals_analysed'' in folder)
#```{r}

df.exp_cf = df.exp %>% 
  select(participant,
         condition,
         contains("cf"))%>% 
  gather("index", "value", -c(participant, condition))%>% 
  filter(value != "") %>%
  arrange(index)%>%
  mutate(scenario = ifelse(condition == 1,"hospital", 
                          ifelse(condition == 2, "garden", 
                          ifelse(condition == 3, "bakery", " "))))%>%
  spread(index, value) %>%
  arrange(participant)

write.csv(df.exp_cf,'Counterfactuals.csv')
#```

##Join dataframe with Analysed Counterfactual Responses Dataframe

```{r}
df.counterfactuals<-read.csv("Counterfactuals_analysed.csv") %>% 
  select(participant, counterfactual_1, counterfactual_2) 
  
df.exp<-df.exp %>% 
inner_join(df.counterfactuals, by="participant") %>% 
filter(counterfactual_1 != "X" ) %>% 
filter(counterfactual_2 != "X")
```

### Demographics

```{r}
####Experiment 4
###Demographics

df.exp_demo <- df.exp %>% 
  select(age, gender, duration) %>% 
  mutate(age=as.numeric(age)) %>%
  transform(gender= ifelse(gender==1, "Male", #recode numbers into gender categories
                    ifelse(gender==2, "Female",
                    ifelse(gender==3, "Prefer not to say", gender)))) %>% 
  filter(age<100 |age ==" ") %>% #remove outliers (year) or N.A.s
  summarize(n=n(),
             female=sum(gender=="Female"),
             not_say=sum(gender=="Prefer not to say"),
             mean_age = mean(age),
             std_age=sd(age),
             mean_time=mean(duration/60),
             sd_time=sd(duration/60)
            )


df.exp_desc <- df.exp_long %>% 
  select(participant, ignorance, counterfactual) %>% 
  group_by(ignorance, counterfactual) %>% 
  summarize(n=n())
```

## Descriptive Statistics: Causal, Knowledge, Blame and Forward-looking Causation Rating


```{r}

##########-------------------------- Descriptives: Between
df.exp_desc_1<- df.exp_long%>%
  group_by(ignorance) %>%
  summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96,
            k_mean = mean(know_rating),
            K_sd   = sd(know_rating), 
            k_upper_ci = k_mean+c_se*1.96, 
            k_lower_ci = k_mean-c_se*1.96,
            b_mean = mean(blame_rating),
            b_sd   = sd(blame_rating),
            b_upper_ci = b_mean+c_se*1.96, 
            b_lower_ci = b_mean-c_se*1.96           
)

##########-------------------------- Descriptives: within

df.exp_desc_2<- df.exp_long2%>%
  group_by(ignorance) %>%
  summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96,
            k_mean = mean(know_rating),
            K_sd   = sd(know_rating), 
            k_upper_ci = k_mean+c_se*1.96, 
            k_lower_ci = k_mean-c_se*1.96,
            b_mean = mean(blame_rating),
            b_sd   = sd(blame_rating),
            b_upper_ci = b_mean+c_se*1.96, 
            b_lower_ci = b_mean-c_se*1.96           
)


##########-------------------------- Descriptives: Forward Looking

df.exp_desc_f<- df.exp_long_f%>%
  group_by( scenario, ignorance) %>%
  summarise(n=n(),
            l_mean = mean(look_rating),#causal rating
            l_sd   = sd(look_rating), 
            o_mean = mean(outcome_rating),
            o_sd   = sd(outcome_rating)
)



```

## Edit and Create dataframe in long format

```{r}
## Create Data in long format

df.exp_long = df.exp %>% 
  select(scenario,
         order,
         participant,
         contains("cause"),
         contains("could"),
         contains("blame"),
          contains("counterfactual_"),
         -starts_with("cf")
         ) %>% 
  gather(condition, rating, "cause_1":"counterfactual_2") %>%  
  mutate(ignorance = ifelse(str_detect(condition, "1"),
                        "reads e-mail", "doesn't read e-mail")) %>% 
  mutate(condition = ifelse(str_detect(condition, "cause"),"causal_rating", 
                                ifelse(str_detect(condition, "could"), "know_rating", 
                                       ifelse(str_detect(condition, "blame"), "blame_rating", "counterfactual"
                                                     )))) %>% 
  spread(condition, rating) %>% 
  mutate(scenario=as.factor(scenario)) %>% 
  mutate(ignorance=as.factor(ignorance)) %>% 
  mutate(causal_rating=as.numeric(causal_rating)) %>% 
  mutate(know_rating=as.numeric(know_rating)) %>% 
  mutate(blame_rating=as.numeric(blame_rating)) %>% 
  mutate(counterfactual=recode(counterfactual, 
                               '1' = "causal action",
                               '2_0' = "epist. change",
                               '2_2_1' = "... by e-mail reading",
                               '2_1' = "... by info" ,
                               '2_2' = "... by info + e-mail reading",
                               '2_3' = "... by other action of agent",
                               '2_4' = "... by someone else",
                               '4' =  "environment" ))%>% 
  mutate(counterfactual=factor(counterfactual, levels=c("epist. change", "... by info", "... by info + e-mail reading", "... by other action of agent", "... by someone else", "causal action", "... by e-mail reading", "environment"))) %>% 
  mutate(ignorance=factor(ignorance, levels= c( "doesn't read e-mail", "reads e-mail")))


```
  
######create Dataframe for Between Subject Analysis

```{r}
####Create Dataframe for between subjects analysis
df.exp_long2 <- df.exp_long %>% 
  filter(order == "doesn't read e-mail first" & ignorance == "doesn't read e-mail" |order == "reads e-mail first" & ignorance == "reads e-mail") 
  
```


### Dataframe just with Counterfactual Responses: Within Contrast

```{r}

df.exp_cf<- df.exp_long %>% 
  select(participant, scenario, order, ignorance, counterfactual) %>% 
   filter(!str_detect(counterfactual, 'causal action')) %>% 
  filter(!str_detect(counterfactual, 'environment')) %>% 
  filter(!str_detect(counterfactual, '... by e-mail reading')) 
  
```

### Dataframe just with Counterfactual Responses: Between Contrast


```{r}
df.exp_cf2<- df.exp_cf%>% 
  filter(order == "doesn't read e-mail first" & ignorance == "doesn't read e-mail" |order == "reads e-mail first" & ignorance == "reads e-mail")
```

#### Descriptives of Counterfactual Descriptives

```{r}

############### Descriptives, Within Contrast

df.exp_cf_desc <- df.exp_long%>% 
  select(scenario, counterfactual, ignorance) %>% 
  group_by(ignorance, counterfactual) %>% 
  summarize(n=n()) %>% 
  ungroup(ignorance) %>% 
  mutate(freq = 
    case_when(ignorance == "doesn't read e-mail" ~ n / 116,
              ignorance == "reads e-mail" ~ n / 125)
  )


############### Descriptives, Between Contrast

df.exp_cf_desc2 <- df.exp_cf2%>% 
  select(scenario, counterfactual, ignorance) %>% 
  group_by(counterfactual, ignorance) %>% 
  summarize(n=n()) %>% 
  ungroup(counterfactual) %>% 
  group_by(ignorance) %>% 
  mutate(total=sum(n),
         freq=n/total)
    
```

### Create Dataframe with Forward Looking Ratings: Epistemic Actions and Outcome Ratings  
  
```{r}

####Forward looking ratings: Reading e-mail and outcome rating

df.exp_long_f = df.exp %>% 
  select(scenario,
         order,
         participant,
         contains("look"),
         contains("outcome"),
         -starts_with("cf"))%>%
  gather(condition, rating, "look_a1":"outcome_a2") %>%  
  mutate(ignorance = ifelse(str_detect(condition, "_a1"),
                        "read e-mail", "didn't read e-mail")) %>% 
  mutate(condition = ifelse(str_detect(condition, "look"),"look_rating", "outcome_rating"
                                              ))%>% 
  spread(condition, rating) %>% 
  mutate(scenario=as.factor(scenario)) %>% 
  mutate(ignorance=as.factor(ignorance)) %>% 
  mutate(look_rating=as.numeric(look_rating)) %>% 
  mutate(outcome_rating=as.numeric(outcome_rating))


```

##### Create Graph for Causal and Counterfactual responses


```{r}

### Set GGplot Theme

myTheme <-   theme(axis.title.x  = element_blank(), 
                   axis.title.y = element_text(color="black", size = 14, vjust=.9), 
                   axis.text.x = element_text(color="black", size = 14),
                   axis.text.y = element_text(color="black", size = 14), 
                   strip.text.x = element_text(color="black", size = 14),
                   legend.text = element_text(color="black", size = 14),
                   legend.position = "top",
                   legend.title = element_blank(),
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))
    


################# Causal Responses

CausalExp4 <- ggplot(df.exp_long, aes(x=ignorance,y=causal_rating, fill = ignorance, colour = ignorance))+
  coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(0, 7, by=1))+
  geom_line(aes(group=participant),position = position_jitter(width = .1), size = 1, alpha=0.1)+ #Create lines between points for each subject
  stat_summary(fun=mean, geom='line',color='black',  group = 1, position = position_nudge(x=.1))+ #Create grand averaged effects line
 # geom_flat_violin(position = position_nudge(x = .1, y = 0),adjust =1.5, alpha=0.5)+
  geom_point(position = position_jitter(width = .1), size = 1, alpha=0.5)+
  stat_summary(fun.data = mean_cl_normal, geom = "pointrange", position = position_nudge(x=.1), colour = "BLACK", width = 0.5,
  size = 1.2, shape = 21, fatten = 2.5)+
  ylab('Score')+xlab('Group')+
  scale_fill_manual(values=c("#999999", "#E69F00"), name="blank", labels=c("Knowledge", "Ignorance"))+
  scale_colour_manual(values=c("#999999", "#E69F00"), name="blank", labels=c("Knowledge", "Ignorance"))+
  labs( y="Causal Rating")+
  theme_bw()+
  guides(fill = FALSE, colour = FALSE) +
  facet_grid(~scenario)+
  myTheme+
  theme(
    axis.text.x = element_text(angle = 12, hjust = 1, color="black", size = 14))
  
CausalExp4
ggsave(CausalExp4, file="Fig4a.pdf", dpi=400, height = 5, width = 8)

##################### Counterfactual Responses

CFExp4<-ggplot(df.exp_cf, aes(x=counterfactual, group=ignorance))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  coord_cartesian(ylim = c(0,1)) +
  scale_y_continuous(labels=scales::percent_format(accuracy = 1), breaks = seq(0, 1, by=0.20)) +
  ylab("proportion of responses") +
  facet_wrap(~ignorance)+
  scale_fill_brewer(palette="Greys", direction=-1)+
  theme_bw()+
  myTheme+
  theme(legend.position= "none")+
  theme(
    axis.text.x = element_text(angle = 25, hjust = 1, color="black", size = 14))

CFExp4
ggsave(CFExp4, file="Fig4b.pdf", dpi=400, height = 5, width = 8)

```
#### Analysis counterfactual Responses: Within Contrast

```{r}

df.exp_cf <- within(df.exp_cf, ignorance <- relevel(ignorance, ref = "reads e-mail"))

library(VGAM)
vglm1 <- vglm(counterfactual ~ ignorance, family=multinomial(refLevel="epist. change"), df.exp_cf)
vglm0 <- vglm(counterfactual ~ +1, family=multinomial(refLevel="epist. change"), df.exp_cf)

#likelihood ratio test null vs factor model 
VGAM::lrtest(vglm0, vglm1)
summary(vglm1)


##odds ratio
exp(coef(vglm1))

####R-Squared
LLf   <- logLik(vglm1)
LL0   <- logLik(vglm0)
as.vector(1 - (LLf / LL0))

```
#### Analysis counterfactual Responses: Between Contrast

```{r}
#df.exp_cf2 <- within(df.exp_cf2, ignorance <- relevel(ignorance, ref = "reads e-mail"))

library(VGAM)
vglm1 <- vglm(counterfactual ~ ignorance, family=multinomial(refLevel="epist. change"), df.exp_cf2)
vglm0 <- vglm(counterfactual ~ +1, family=multinomial(refLevel="epist. change"), df.exp_cf2)

#likelihood ratio test null vs factor model 
VGAM::lrtest(vglm0, vglm1)
summary(vglm1)

##odds ratio
exp(coef(vglm1))

####R-Squared
LLf   <- logLik(vglm1)
LL0   <- logLik(vglm0)
as.vector(1 - (LLf / LL0))
```

```{r}
######Subgroup Analysis

myTheme <-   theme(plot.title=element_text(size=18, 
                                    face="bold", 
                                    hjust=0.5,
                                    lineheight=1.2),
                   axis.title.y = element_text(color="black", size = 14, vjust=.9),
                   axis.title.x = element_text(color="black", size = 14, vjust=.9), 
                   axis.text.x =  element_text(color="black", size = 14, vjust=.9),
                   axis.text.y = element_text(color="black", size = 14), 
                   strip.text.x = element_text(color="black", size = 14),
                   legend.text = element_text(color="black", size = 14),
                   legend.title = element_text(color="black", size = 14),
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))

#### create text plot
df.text <- data.frame(
  ignorance = c("doesn't read e-mail", "doesn't read e-mail", "doesn't read e-mail", "reads e-mail","reads e-mail", "reads e-mail" ),
  counterfactual = c("... by info", "... by info + e-mail reading", "... by other action of agent", "... by info", "... by info + e-mail reading", "... by other action of agent" ),
  N = c("N = 8", "N = 46", "N = 35", "N = 82", NA, "N = 25")
  )

#### create plot
Fig4c = df.exp_long %>% 
    filter(counterfactual=="... by other action of agent" | counterfactual=="... by info"  | counterfactual=="... by info + e-mail reading") %>% 
  ggplot(aes(x=counterfactual, y=causal_rating, fill=counterfactual)) + 
  coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(0, 7, by=1))+
  geom_jitter(height = 0.1, width = 0.1, alpha =  0.3, colour = "grey")+
  stat_summary(fun.data = mean_cl_boot, geom = "pointrange", position = position_dodge(width = 0.8), width = 0.2,
  size = 1, shape = 21) + 
  scale_fill_manual(values=c("gray42", "gray72", "gray99"), name="blank")+
  facet_wrap(~ignorance)+
  geom_text(data= df.text,
           aes(label = N,
               y = 6.5,
               x = counterfactual)
          ) +
  labs(x= "Epistemic state change")+
  labs(y="Causal Rating")+
  labs(title="Epistemic Action")+
  theme_bw()+
  myTheme+
  theme(axis.text.x = element_text(angle = 15, hjust = 1, color="black", size = 14),
          legend.position= "none")

           
Fig4c
########save plot
ggsave(Fig4c, file="Fig4c.pdf", dpi=400, height = 5, width = 8)


```

##### Subgroup Analysis of Counterfactual Responses: Within Subject Contrast

```{r}
####### Analysis
### Causal Ratings according to Countefactual Category

library("car")
library("emmeans")
library("afex")

################### Within Subject Contrast 

df.exp_subgroup <- df.exp_long %>% 
   filter(counterfactual== "... by info" | counterfactual=="... by info + e-mail reading" | counterfactual=="... by other action of agent" )

### Full model 

mixed(causal_rating ~ ignorance+counterfactual + (1 | participant), df.exp_subgroup, method = 'LRT')

S4  <- lmer(causal_rating ~  counterfactual *ignorance+ (1 | participant),df.exp_subgroup, REML=T)

##### Posthoc Test
S4_posthoc = emmeans(S4, specs = pairwise ~ counterfactual | ignorance)
summary(S4_posthoc)

##### Descriptives

df.exp_subgroup_desc <- df.exp_subgroup %>% 
  group_by(ignorance, counterfactual) %>% 
   summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96)

```


##### Subgroup Analysis of Counterfactual Responses: Between Subject Contrast
```{r}
################### Between Subject Contrast 

df.exp_subgroup2 <- df.exp_long2 %>% 
   filter(counterfactual== "... by info" | counterfactual=="... by info + e-mail reading" | counterfactual=="... by other action of agent" )

S3  <- lm(causal_rating ~ counterfactual + ignorance, df.exp_subgroup2)
S3 %>% Anova()

####post hoc tests

S4  <- lm(causal_rating ~ counterfactual*ignorance, df.exp_subgroup2)
S4 %>% Anova()
S4_posthoc <- emmeans(S4, pairwise ~ counterfactual |ignorance)
summary(S4_posthoc)

##### Descriptives

df.exp_desc_subgroup2<- df.exp_subgroup2 %>%
  group_by(ignorance, counterfactual) %>%
  summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96
  )
```
#### Create Knowledge and Blame Rating Plot

```{r}

######Knowledge and Blame plot

library("ggpubr")



myTheme <-   theme(axis.title.x  = element_blank(), 
                   axis.title.y = element_text(color="black", size = 14), 
                   axis.text.x = element_text(color="black", size = 14),
                   axis.text.y = element_text(color="black", size = 14), 
                   strip.text.x = element_text(color="black", size = 14),
                   legend.text = element_text(color="black", size = 14),
                   legend.position = "top",
                   legend.title = element_blank(),
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))

##### Knowledge Bar Plot
Plot1<- ggplot(df.exp_long, aes(x=ignorance, y=know_rating, fill=ignorance)) + 
 coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(1, 7, by=1))+
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha=0.5) +
  stat_summary( fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.90), width = 0.2) +
  geom_jitter(position = position_jitterdodge(jitter.height = 0.2, dodge.width = 0.90, jitter.width=0.15), alpha = 
  0.3, colour="grey")+
    scale_fill_manual(values=c("lightyellow4", "gold"))+
  #scale_fill_brewer(palette="Dark2")+
  labs( y="Could have known Rating")+
  theme_bw()+
  myTheme

Plot1

##### Blame Bar Plot

Plot2 <- ggplot(df.exp_long, aes(x=ignorance, y=blame_rating, fill=ignorance)) + 
 coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(1, 7, by=1))+
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha=0.5) +
  stat_summary( fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.90), width = 0.2) +
  geom_jitter(position = position_jitterdodge(jitter.height = 0.2, dodge.width = 0.90, jitter.width=0.15), alpha = 
  0.3, colour="grey")+
    scale_fill_manual(values=c("ivory3", "khaki"))+
  #scale_fill_brewer(palette="Dark2")+
  labs( y="Blame for Ignorance Rating")+
  theme_bw()+
  myTheme

Plot2

##### Causal - Knowledge Regression Plot

Plot3<- ggplot(df.exp_long, aes(x=know_rating, y=causal_rating, fill=ignorance, colour= ignorance)) + 
 coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(1, 7, by=1))+
    scale_x_continuous(breaks = seq(1, 7, by=1))+
  stat_smooth(method = "lm", col = "black", fullrange=F,aes(fill=ignorance)) +
  #geom_jitter(position = position_jitterdodge(jitter.height = 0.2, dodge.width = 0.90, jitter.width=0.15), alpha = 
  #0.3, colour="grey")+
    scale_fill_manual(values=c("lightyellow4", "gold"))+
  #scale_fill_brewer(palette="Dark2")+
  labs( y="Causal Rating", x ="Could have known Rating")+
  theme_bw()+
  myTheme+
  theme(axis.title.x  = element_text(color="black", size = 14, vjust=.9))

Plot3

#### Blame - Knowledge regression plot

Plot4<- ggplot(df.exp_long, aes(x=know_rating, y=blame_rating, fill=ignorance, colour= ignorance)) + 
 coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(1, 7, by=1))+
    scale_x_continuous(breaks = seq(1, 7, by=1))+
  stat_smooth(method = "lm", col = "black", fullrange=F,aes(fill=ignorance)) +
  #geom_jitter(position = position_jitterdodge(jitter.height = 0.2, dodge.width = 0.90, jitter.width=0.15), alpha = 
  #0.3, colour="grey")+
    scale_fill_manual(values=c("ivory3", "khaki"))+
  #scale_fill_brewer(palette="Dark2")+
  labs( y="Blame for Ignorance Rating", x = "Could have known Rating")+
  theme_bw()+
  myTheme+
  theme(axis.title.x  = element_text(color="black", size = 14, vjust=.9))

Plot4

### merge plots with `read e-mail' and `no reading of e-mail' condition
Fig4d <- ggarrange(Plot1, Plot2, Plot3, Plot4,
                    ncol = 2, 
                    nrow = 2)
### show plot
plot(Fig4d)

### save plot
ggsave(Fig4d, file="Fig4d.pdf", dpi=400, height = 8, width = 8)


```
#### Analysis Causal Ratings


```{r}
### Experiment 4: Causal Ratings


library("car")
library("afex")

mixed(causal_rating ~ 1 + ignorance*scenario +  (1 | participant), df.exp_long, method = 'LRT')
C4  <- lmer(causal_rating ~ 1 + ignorance*scenario + (1 | participant), df.exp_long, REML=T)
summary(C4)


##Post-Hoc Test: Ignorance
emmeans(C4, list(pairwise ~ ignorance), adjust = "tukey")

################### Between Contrasts

C4  <- lm(causal_rating ~ ignorance*scenario , df.exp_long2)
C4 %>% Anova()

####post hoc tests
C4_posthoc <- emmeans(C4, pairwise ~ ignorance)
summary(C4_posthoc)

```
### Analysis Knowledge Ratings

```{r}
### Experiment 4: Knowledge Ratings

############ Within Contrasts 
mixed(know_rating ~ 1 + ignorance*scenario +  (1 | participant), df.exp_long, method = 'LRT')
K4  <- lmer(know_rating ~ 1 + ignorance*scenario + (1 | participant), df.exp_long, REML=T)
summary(K4)

###Parwise T test for ignorance
emmeans(K4, list(pairwise ~ ignorance))

##############WBetween Contrasts 
K4b  <- lm(know_rating ~ 1 + ignorance*scenario , df.exp_long2)
K4b %>% Anova()



####post hoc tests
K4b_posthoc <- emmeans(K4b, pairwise ~ ignorance)
summary(K4b_posthoc)

```
#### Analysis Blame for Ignorance Ratings

```{r}
######Blame Rating
########## Within Contrasts 

mixed(blame_rating ~ 1 + ignorance*scenario +  (1 | participant), df.exp_long, method = 'LRT')
B4  <- lmer(blame_rating ~ 1 + ignorance*scenario + (1 | participant), df.exp_long, REML=T)
summary(B4)


########## Between Contrasts 

B4b  <- lm(blame_rating ~ 1 + ignorance*scenario , df.exp_long2)
B4b %>% Anova()

####post hoc tests
B4b_posthoc <- emmeans(B4b, pairwise ~ ignorance)
summary(B4b_posthoc)


```
#### Analysis Blame and Knowledge Regression

```{r}

############## Within subject contrast
mixed(causal_rating ~ignorance*know_rating + (1 | participant), df.exp_long, method = 'LRT')
K4R  <- lmer(causal_rating ~ignorance*know_rating + (1 | participant), df.exp_long, REML=T)

summary(K4R)

mixed(blame_rating ~ignorance*know_rating + (1 | participant), df.exp_long, method = 'LRT')
B4R  <- lmer(blame_rating ~ignorance*know_rating + (1 | participant), df.exp_long, REML=T)

summary(B4R)

############ Between subject contrast

K4Rb  <- lm(causal_rating ~ignorance*know_rating , df.exp_long2)
K4Rb %>% Anova()

summary(K4Rb)

B4Rb  <- lm(blame_rating ~ignorance*know_rating , df.exp_long2)
B4Rb %>% Anova()

summary(B4Rb)
```
#### Plot of Future E-mail Reading and OUtcome Likelihood Rating

```{r}
############Plot Likelihood of future reading and outcome rating

#### create subdataframe with Descriptives
df.ci<-df.exp_long_f %>% 
  group_by(ignorance) %>% 
  summarise(
    m_look=mean(look_rating),
    m_outcome=mean(outcome_rating),
    l_sd   = sd(look_rating), 
    l_se   = l_sd / sqrt(n()), 
    l_upper_ci = m_look+l_se*1.96, 
    l_lower_ci = m_look-l_se*1.96,
    o_sd   = sd(outcome_rating), 
    o_se   = o_sd / sqrt(n()), 
    o_upper_ci = m_outcome+o_se*1.96, 
    o_lower_ci = m_outcome-o_se*1.96
  )
  
  
###### create plot
Fig4e<-  ggplot(df.exp_long_f, aes(x=look_rating, y=outcome_rating, group=ignorance, color=ignorance)) +
  geom_point(size=2, position = "jitter", width = 0.5, height = 0.4, alpha = 0.3) + 
  #geom_errorbarh( aes(xmin = l_lower_ci,xmax = o_upper_ci))+
  geom_point(data=df.mean, size=6, shape=17) + 
  #geom_linerange(data=df.ci, aes(xmin = l_lower_ci,xmax = l_upper_ci))+
  theme_bw()+
  #theme_cowplot()+
  scale_fill_manual(values=c("#999999", "#E69F00"), name="blank")+
  scale_colour_manual(values=c("#999999", "#E69F00"), name="blank")+
  xlab("Likelihood of reading future e-mail") + ylab("Likelihood of future outcome")+
  theme(axis.title.x  = element_text(color="black", size = 14, vjust=.9), 
                   axis.title.y = element_text(color="black", size = 14), 
                   axis.text.x = element_text(color="black", size = 14),
                   axis.text.y = element_text(color="black", size = 14), 
                   strip.text.x = element_text(color="black", size = 14),
                   legend.text = element_text(color="black", size = 14),
                   legend.position = "top",
                   legend.direction = "horizontal",
                   legend.title = element_blank(),
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))+
  guides(shape=guide_legend(title.position="bottom",
                            legend.title.align = 0.9
                            ))

Fig4e
###save plot
ggsave(Fig4e, file="Fig4e.pdf", dpi=400, height = 5, width = 6)

```
#### Analysis Future E-mail Reading and OUtcome Likelihood Rating
```{r}
### Experiment 4: Likelhood of reading and future outcome rating


###### Reading Rating
L4  <- lm(look_rating ~ 1 + ignorance*scenario, df.exp_long_f)
anova(L4)
summary(L4)

###### Outcome Rating
O4  <- lm(outcome_rating ~ 1 + ignorance*scenario, df.exp_long_f)
anova(O4)
summary(O4)


```

### Descriptives Future E-mail Reading and OUtcome Likelihood Rating

```{r}

df.exp_descf_ratings<- df.exp_long_f%>%
  group_by(ignorance) %>%
  summarise(r_mean = mean(look_rating),#causal rating
            r_sd   = sd(look_rating), 
            r_se   = r_sd / sqrt(n()), 
            r_upper_ci = r_mean+r_se*1.96, 
            r_lower_ci = r_mean-r_se*1.96,
            o_mean = mean(outcome_rating),#could have known rating
            o_sd   = sd(outcome_rating), 
            o_se   = o_sd / sqrt(n()), 
            o_upper_ci = o_mean+o_se*1.96, 
            o_lower_ci = o_mean-o_se*1.96
  )
```






