---

author: "Lara Kirfel & David Lagnado"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    theme: cosmo
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  comment = "",
  results = "hold",
  fig.show = "hold")
```

# Install packages

```{r, message=FALSE}
install.packages("pastecs");
install.packages("reshape")
install.packages("lubridate")
install.packages("lsr")
install.packages("janitor")
install.packages("DT")
install.packages("Hmisc")
install.packages("broom")
install.packages("tidyverse")
install.packages("ez")
install.packages("schoRsch")
install.packages("stringr")
install.packages("emmeans")
install.packages("car")

```

# Load packages 

```{r, message=FALSE}
library("pastecs")
library("reshape")
library("knitr")
library("lubridate")
library("lsr")
library("janitor") # for cleaning variable names 
library("DT") # for nice tables
library("Hmisc") # for smean function for bootstrapped confidence intervals 
library("broom") # for tidy regression results
library("tidyverse") # for data wrangling, visualization, etc. 
library("ez")
library("schoRsch")
library("lme4")
library("stringr")
library("dplyr")
library("nlme")
library("ggpubr")

```

```{r}
# set ggplot theme 
theme_set(
  theme_classic()
)
```

# Experiment 3:

## Read in Data

```{r}
df.data = read.csv(file = "EpStates_3.csv", stringsAsFactors = F, sep = ",") %>% 
  filter(row_number() > 2) %>% # additional rows in qualtrics csv
  clean_names() %>% 
  filter(distribution_channel != "preview",
         !condition =="", #exclude bot fails,
          progress ==100| progress==99|progress==98)
 
```

## Structure and edit data

```{r}

df.exp = df.data %>% 
  mutate(participant = 1:n()) %>% 
  rename(duration=duration_in_seconds) %>% 
  mutate(duration=as.numeric(duration)) %>% 
  select(h_check_fact_1:b_b_2_1,
         participant,
         order,
         duration,
         condition,
         gender,
         age,
         -starts_with("q")
         ) %>% 
  gather("index", "value", -c(age, gender, participant, condition, duration, order))%>% 
  filter(value != "") %>%
  arrange(index)%>%
  mutate(index = ifelse(str_detect(index,"_c_1"),
                        "cause_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_c_2"),
                        "cause_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_k_1"),
                        "could_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_k_2"),
                        "could_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_b_1"),
                        "blame_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_b_2"),
                        "blame_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_cf_1"),
                        "cf_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"_cf_2"),
                        "cf_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"fact_1"),
                        "fact_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"fact_2"),
                        "fact_2",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"know_1"),
                        "know_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"know_2"),
                        "know_2",
                        index)) %>% 
  mutate(index = ifelse(str_detect(index,"test_1"),
                        "test_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"test_2"),
                        "test_2",
                        index)) %>%
  mutate(index = ifelse(str_detect(index,"read_1"),
                        "read_1",
                        index))%>% 
  mutate(index = ifelse(str_detect(index,"read_2"),
                        "read_2",
                        index)) %>%
  mutate(order = ifelse(order == 1,"many actions first", 
                          ifelse(order == 2, "few actions first", " ")))%>%
  mutate(scenario = ifelse(condition == 1,"Hospital", 
                          ifelse(condition == 2, "Garden", 
                          ifelse(condition == 3, "Bakery", " "))))%>%
  spread(index, value) %>%
  arrange(participant)

```


##### Filter participants

```{r}
####Experiment 3: Create filter
df.exp<- df.exp%>%  
  mutate(check_total=if_else(know_1=="2", 1, 0)) %>% 
  mutate(check_total=if_else(know_2 =="2", check_total+1, check_total)) %>% 
  mutate(check_total=if_else(fact_1 =="1", check_total+1, check_total)) %>% 
  mutate(check_total=if_else(fact_2=="1",  check_total+1, check_total)) %>% 
  mutate(check_total=if_else(read_1=="1",  check_total+1, check_total)) %>% 
  mutate(check_total=if_else(read_2=="1",  check_total+1, check_total)) %>% 
  mutate(check_total=if_else(test_1=="1",  check_total+1, check_total)) %>% 
  mutate(check_total=if_else(test_2=="2",  check_total+1, check_total))


#### Set filter
df.exp<-df.exp %>% 
  filter(check_total ==8) 
```


##### Export Counterfactual Responses for separate analysis (see analysed datasheet ``Counterfactuals_analysed'' in folder)

#```{r}

df.exp_cf = df.exp %>% 
  select(participant,
         condition,
         contains("cf"))%>% 
  gather("index", "value", -c(participant, condition))%>% 
  filter(value != "") %>%
  arrange(index)%>%
  mutate(scenario = ifelse(condition == 1,"hospital", 
                          ifelse(condition == 2, "garden", 
                          ifelse(condition == 3, "bakery", " "))))%>%
  spread(index, value) %>%
  arrange(participant)

write.csv(df.exp_cf,'Counterfactuals.csv')
#```

##Join dataframe with Analysed Counterfactual Responses Dataframe

```{r}
df.counterfactuals<-read.csv("Counterfactuals_analysed.csv") %>% 
  select(participant, counterfactual_1, counterfactual_2) 
  
df.exp<-df.exp %>% 
inner_join(df.counterfactuals, by="participant") %>% 
filter(counterfactual_1 != "0" | counterfactual_2 != "0")
```

### Demographics
```{r}
####Experiment 3
###Demographics

df.exp_demo <- df.exp %>% 
  select(age, gender, duration) %>% 
  mutate(age=as.numeric(age)) %>%
  transform(gender= ifelse(gender==1, "Male", #recode numbers into gender categories
                    ifelse(gender==2, "Female",
                    ifelse(gender==3, "Prefer not to say", gender)))) %>% 
  filter(age<100 |age ==" ") %>% #remove outliers (year) or N.A.s
  summarize(n=n(),
             female=sum(gender=="Female"),
             not_say=sum(gender=="Prefer not to say"),
             mean_age = mean(age),
             std_age=sd(age),
             mean_time=mean(duration/60),
             sd_time=sd(duration/60)
            )

####### Descriptives
df.exp_desc <- df.exp %>% 
  select(participant, scenario) %>% 
  group_by(scenario) %>% 
  summarize(n=n())
```

## Edit and Create dataframe in long format

```{r}
## Long format

df.exp_long = df.exp %>% 
  select(scenario,
         order,
         participant,
         contains("cause"),
         contains("could"),
         contains("blame"),
         contains("counterfactual_"))%>%
  gather(condition, rating, "cause_1":"counterfactual_2") %>%  
  mutate(ignorance = ifelse(str_detect(condition, "1"),
                        "many actions", "few actions")) %>% 
  mutate(condition = ifelse(str_detect(condition, "cause"),"causal_rating", 
                                ifelse(str_detect(condition, "could"), "know_rating", 
                                       ifelse(str_detect(condition, "blame"), "blame_rating", "counterfactual"
                                                     )))) %>% 
  spread(condition, rating) %>% 
  mutate(scenario=as.factor(scenario)) %>% 
  mutate(ignorance=as.factor(ignorance)) %>% 
  mutate(causal_rating=as.numeric(causal_rating)) %>% 
  mutate(know_rating=as.numeric(know_rating)) %>% 
  mutate(blame_rating=as.numeric(blame_rating)) %>% 
  mutate(counterfactual=recode(counterfactual, 
                               '1' = "causal action",
                               '2_0' = "epistemic change",
                               '2_1' = "... by reading (at least) one more" ,
                               '2_2' = "... by reading all e-mails",
                               '2_3' = "... by other",
                               '2_4' = "... by other",
                               '3' = "... by other",
                               '4' =  "environment" )) %>% 
  mutate(counterfactual=factor(counterfactual, levels=c("causal action", "epistemic change", "... by reading (at least) one more", "... by reading all e-mails", "... by other", "environment", "X")))
  
```

####Create Dataframe with Counterfactual responses: Within Contrast 

```{r}

### Dataframe just with CF Responses (non-sensical deleted)


df.exp_cf<- df.exp_long %>% 
  select(participant, scenario, order, ignorance, counterfactual) %>% 
  reshape(v.names="counterfactual", timevar="ignorance", idvar=c("participant", "scenario", "order"),
        direction="wide") %>% 
  filter(`counterfactual.few actions` != "X" ) %>% ###delete those participants who selected a non-sensical answer
  reshape(idvar=c("participant", "scenario", "order"), 
        sep = ".", direction = "long") %>%  ###reshape back into long format
  remove_rownames() 

```

####Create Dataframe with Counterfactual responses: Between Contrast 

```{r}

### Create Dataframe just with CF Responses for between analsyis
df.exp_cf2<- df.exp_cf%>% 
  filter(order == "few actions first" & ignorance == "few actions" |order == "many actions first" & ignorance == "many actions")
```


##### Create Graph for Causal and Counterfactual responses

```{r}
### Set GGplot Theme

myTheme <-   theme(axis.title.x  = element_blank(), 
                   axis.title.y = element_text(color="black", size = 14, vjust=.9), 
                   axis.text.x = element_text(color="black", size = 14),
                   axis.text.y = element_text(color="black", size = 14), 
                   strip.text.x = element_text(color="black", size = 14),
                   legend.text = element_text(color="black", size = 14),
                   legend.position = "top",
                   legend.title = element_blank(),
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))

################# Causal Responses

CausalExp3 <- ggplot(df.exp_long, aes(x=ignorance,y=causal_rating, fill = ignorance, colour = ignorance))+
  coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(0, 7, by=1))+
  geom_line(aes(group=participant),position = position_jitter(width = .1), size = 1, alpha=0.1)+ #Create lines between points for each subject
  stat_summary(fun=mean, geom='line',color='black',  group = 1, position = position_nudge(x=.1))+ #Create grand averaged effects line
  geom_point(position = position_jitter(width = .1), size = 1, alpha=0.5)+
  stat_summary(fun.data = mean_cl_normal, geom = "pointrange", position = position_nudge(x=.1), colour = "BLACK", width = 0.5,
  size = 1.2, shape = 21, fatten = 2.5)+
  ylab('Score')+xlab('Group')+
  scale_fill_manual(values=c("#999999", "#E69F00"), name="blank", labels=c("Knowledge", "Ignorance"))+
  scale_colour_manual(values=c("#999999", "#E69F00"), name="blank", labels=c("Knowledge", "Ignorance"))+
  labs( y="Causal Rating")+
  theme_bw()+
  guides(fill = FALSE, colour = FALSE) +
  facet_grid(~scenario)+
  myTheme+
  theme(axis.text.x = element_text(angle = 15, hjust = 1, color="black", size = 12))

CausalExp3
### Export Figure
ggsave(CausalExp3, file="Fig3a.pdf", dpi=400, height = 5, width = 8)


################# Causal Responses

CFExp3<-ggplot(df.exp_cf2, aes(x=counterfactual, group=ignorance))+
  geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") + 
  coord_cartesian(ylim = c(0,1)) +
  scale_y_continuous(labels=scales::percent_format(accuracy = 1), breaks = seq(0, 1, by=0.20)) +
  ylab("proportion of responses") +
  facet_wrap(~ignorance)+
  scale_fill_brewer(palette="Greys", direction=-1)+
  theme_bw()+
  myTheme+
  theme(legend.position= "none")+
  theme(
    axis.text.x = element_text(angle = 25, hjust = 1, color="black", size = 14))

CFExp3
ggsave(CFExp3, file="Fig3b.pdf", dpi=400, height = 5, width = 8)

```

##### Descriptives for Counterfactual responses, Within Contrast
```{r}
######### Counterfactual Descriptives

df.exp_cf_desc <- df.exp_cf%>% 
  select(scenario, counterfactual, ignorance) %>% 
  group_by(counterfactual) %>% 
  summarize(n=n()) %>% 
  #ungroup(counterfactual) %>% 
  mutate(total=sum(n)/2,
         freq=n/total)

```

### Descriptives for Counterfactual responses, Between Contrast
```{r}
###### Counterfactual Descriptives

df.exp_cf_desc2 <- df.exp_cf2%>% 
  select(scenario, counterfactual, ignorance) %>% 
  group_by(counterfactual, ignorance) %>% 
  summarize(n=n()) %>% 
  ungroup(counterfactual) %>% 
  group_by(ignorance) %>% 
  mutate(total=sum(n),
         freq=n/total)

```

#### Descriptives Causal, Knowledge and Blame Ratings
```{r}
df.exp_desc_ratings<- df.exp_long%>%
  group_by(ignorance) %>%
  summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96,
            k_mean = mean(know_rating),#could have known rating
            k_sd   = sd(know_rating), 
            k_se   = k_sd / sqrt(n()), 
            k_upper_ci = k_mean+c_se*1.96, 
            k_lower_ci = k_mean-c_se*1.96,
            b_mean = mean(blame_rating),#blame rating
            b_sd   = sd(blame_rating), 
            b_se   = b_sd / sqrt(n()), 
            b_upper_ci = b_mean+c_se*1.96, 
            b_lower_ci = b_mean-c_se*1.96
  )
```


#### Analysis Causal Ratings

```{r}
### Experiment 3: Causal Ratings
library(afex)
library(car)

df.exp_long <- within(df.exp_long, ignorance <- relevel(ignorance, ref = 'many actions'))
df.exp_long <- within(df.exp_long, scenario<- relevel(scenario, ref = 'Bakery'))


################### Within Contrasts

mixed(causal_rating ~ 1 + ignorance*scenario +  (1 | participant), df.exp_long, method = 'LRT')
C3  <- lmer(causal_rating ~ 1 + ignorance*scenario + (1 | participant), df.exp_long, REML=T)
summary(C3)

##Post-Hoc Test: Ignorance
emmeans(C3, list(pairwise ~ ignorance), adjust = "tukey")

################### Between Contrasts

C3  <- lm(causal_rating ~ 1 + ignorance*scenario, df.exp_long2)
C3 %>% Anova()

####post hoc tests
C3_posthoc <- emmeans(C3, pairwise ~ ignorance | scenario)
summary(C3_posthoc)


```

### Analysis Knowledge Ratings

```{r}
### Experiment 3: Knowledge Ratings

df.exp_long <- within(df.exp_long, ignorance <- relevel(ignorance, ref = 'few actions'))
df.exp_long <- within(df.exp_long, scenario<- relevel(scenario, ref = 'Bakery'))


################### Within Contrasts

mixed(know_rating ~ 1 + ignorance*scenario +  (1 | participant), df.exp_long, method = 'LRT')
K3  <- lmer(know_rating ~ 1 + ignorance*scenario + (1 | participant), df.exp_long, REML=T)
summary(K3)

##Post-Hoc Test: Ignorance
emmeans(K3, list(pairwise ~ ignorance), adjust = "tukey")


################### Between Contrasts

K3  <- lm(know_rating ~ 1 + ignorance*scenario , df.exp_long2)
K3 %>% Anova()

####post hoc tests
K3_posthoc <- emmeans(K3, pairwise ~ ignorance|scenario)
summary(K3_posthoc)

```

#### Analysis Blame for Ignorance Rating

```{r}
### Experiment 3: Blame Ratings


mixed(blame_rating ~ 1 + ignorance*scenario +  (1 | participant), df.exp_long, method = 'LRT')
B3  <- lmer(blame_rating ~ 1 + ignorance*scenario + (1 | participant), df.exp_long, REML=T)
summary(B3)

##Post-Hoc Test: Ignorance
emmeans(B3, list(pairwise ~ ignorance), adjust = "tukey")

################### Between Contrasts

B3  <- lm(blame_rating ~ 1 + ignorance*scenario , df.exp_long2)
B3 %>% Anova()

####post hoc tests
B3_posthoc <- emmeans(B3, pairwise ~ ignorance)
summary(B3_posthoc)

```

#### Analysis Blame and Knowledge Rating Regression


```{r}
######## Within Suject analysis

mixed(causal_rating ~ignorance*know_rating + (1 | participant), df.exp_long, method = 'LRT')
K3R  <- lmer(causal_rating ~ignorance*know_rating + (1 | participant), df.exp_long, REML=T)

mixed(blame_rating ~ignorance*know_rating + (1 | participant), df.exp_long, method = 'LRT')
B3R  <- lmer(blame_rating ~ignorance*know_rating + (1 | participant), df.exp_long, REML=T)

summary(B3R)

#########between subject contrast
  
K3Rb  <- lm(causal_rating ~ignorance*know_rating , df.exp_long2)
K3Rb %>% Anova()

summary(K3Rb)

B3Rb  <- lm(blame_rating ~ignorance*know_rating , df.exp_long2)
B3Rb %>% Anova()

summary(B3Rb)


```

###### Counterfactual Responses Analysis, Within Contrast

```{r}

########### Counterfactual Responses

df.exp_cf <- within(df.exp_cf, ignorance <- relevel(ignorance, ref = 'many actions'))

library(VGAM)
vglm1 <- vglm(counterfactual ~ ignorance, family=multinomial(refLevel="causal action"), df.exp_cf)
vglm0 <- vglm(counterfactual ~ +1, family=multinomial(refLevel="causal action"), df.exp_cf)

#likelihood ratio test null vs factor model 
VGAM::lrtest(vglm0, vglm1)
summary(vglm1)


##odds ratio
exp(coef(vglm1))

####R-Squared
LLf   <- logLik(vglm1)
LL0   <- logLik(vglm0)
as.vector(1 - (LLf / LL0))


```


###### Counterfactual Responses Analysis, Between Contrast

```{r}

#### Counterfactual Responses

######################Between Contrast

df.exp_cf2 <- within(df.exp_cf2, ignorance <- relevel(ignorance, ref = 'many actions'))


library(VGAM)
vglm1 <- vglm(counterfactual ~ ignorance, family=multinomial(refLevel="causal action"), df.exp_cf2)
vglm0 <- vglm(counterfactual ~ +1, family=multinomial(refLevel="causal action"), df.exp_cf2)

#likelihood ratio test null vs factor model 
VGAM::lrtest(vglm0, vglm1)
summary(vglm1)


##odds ratio
exp(coef(vglm1))

####R-Squared
LLf   <- logLik(vglm1)
LL0   <- logLik(vglm0)
as.vector(1 - (LLf / LL0))
```

#### Create Graph for Causal Rating by Counterfactual Response Subgroup Analysis

```{r}
#### Analysing Causal etc. Ratings according to Counterfactual Response category
myTheme <-   theme(plot.title=element_text(size=18, 
                                    face="bold", 
                                    hjust=0.5,
                                    lineheight=1.2),
                   axis.title.y = element_text(color="black", size = 14, vjust=.9),
                   axis.title.x = element_text(color="black", size = 14, vjust=.9), 
                   axis.text.x =  element_text(color="black", size = 14, vjust=.9),
                   axis.text.y = element_text(color="black", size = 14), 
                   strip.text.x = element_text(color="black", size = 14),
                   legend.text = element_text(color="black", size = 14),
                   legend.title = element_text(color="black", size = 14),
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))

###### create text dataframe

df.text <- data.frame(
  ignorance = c("few actions", "few actions", "many actions",  "many actions"),
  counterfactual = c("... by reading (at least) one more" , "... by reading all e-mails", "... by reading (at least) one more" , "... by reading all e-mails" ),
  N = c("N = 28", "N = 49", "N = 1", "N = 72")
  )

###### create graph

Fig3c <- df.exp_long %>% 
  filter(counterfactual=="... by reading (at least) one more" | counterfactual=="... by reading all e-mails") %>% 
   ggplot(aes(x=counterfactual, y=causal_rating, fill=counterfactual)) + 
  coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(0, 7, by=1))+
  geom_jitter(height = 0.1, width = 0.1, alpha =  0.3, colour = "grey")+
  stat_summary(fun.data = mean_cl_boot, geom = "pointrange", position = position_dodge(width = 0.8), width = 0.2,
  size = 1, shape = 21) + 
  #geom_violin(trim=F, scale = "count", adjust = 3, position=position_dodge(width=0.8), alpha=0.1, color = NA)+
  scale_fill_manual(values=c("gray42", "gray72"), name="blank")+
  facet_wrap(~ignorance)+
  geom_text(data= df.text,
           aes(label = N,
               y = 3.5,
               x = counterfactual)
          ) +
  labs(x= "Epistemic state change")+
  labs(y="Causal Rating")+
  labs(title="Epistemic Actions")+
  theme_bw()+
  myTheme+
  theme(axis.text.x = element_text(angle = 15, hjust = 0.95, color="black", size = 14),
          legend.position= "none")


Fig3c

####### export figure
ggsave(Fig3c, file="Fig3c.pdf", dpi=400, height = 5, width = 8)


```

### Subgroup Analysis: Causal Ratings according to Countefactual Category
##### Within Subject Contrast 

```{r}

library("car")
library("afex")

################### Within Subject Contrast 
df.exp_subgroup <- df.exp_long %>% 
   filter(counterfactual=="... by reading (at least) one more" | counterfactual=="... by reading all e-mails")

mixed(causal_rating ~ ignorance+counterfactual + (1 | participant), df.exp_subgroup, method = 'LRT')

S1  <- lmer(causal_rating ~  counterfactual *ignorance+ (1 | participant),df.exp_subgroup, REML=T)


####Post hoc tests

S1_posthoc = emmeans(S1, specs = pairwise ~ counterfactual | ignorance)
summary(S1_posthoc)


################### Descriptives

df.exp_desc_subgroup<- df.exp_subgroup %>%
  group_by(ignorance, counterfactual) %>%
  summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96
  )


```

### Subgroup Analysis: Causal Ratings according to Countefactual Category
##### Between Subject Contrast 


```{r}
################### Between Subject Contrast 

df.exp_subgroup2 <- df.exp_long2 %>% 
      filter(counterfactual=="... by reading (at least) one more" | counterfactual=="... by reading all e-mails")

S3  <- lm(causal_rating ~  ignorance + counterfactual, df.exp_subgroup2)
S3 %>% Anova()

####Post hoc tests

S4  <- lm(causal_rating ~ counterfactual*ignorance, df.exp_subgroup2)
S4 %>% Anova()
S4_posthoc <- emmeans(S4, pairwise ~ counterfactual |ignorance)
summary(S4_posthoc)

################### Descriptives

df.exp_desc_subgroup2<- df.exp_subgroup2 %>%
  group_by(ignorance, counterfactual) %>%
  summarise(c_mean = mean(causal_rating),#causal rating
            c_sd   = sd(causal_rating), 
            c_se   = c_sd / sqrt(n()), 
            c_upper_ci = c_mean+c_se*1.96, 
            c_lower_ci = c_mean-c_se*1.96
  )
```

#### Plot for Knowlede and Blame Ratings

```{r}

######Knowledge and Blame plot

myTheme <-   theme(axis.title.x  = element_blank(), 
                   axis.title.y = element_text(color="black", size = 14), 
                   axis.text.x = element_text(color="black", size = 14),
                   axis.text.y = element_text(color="black", size = 14), 
                   strip.text.x = element_text(color="black", size = 14),
                   legend.text = element_text(color="black", size = 14),
                   legend.position = "top",
                   legend.title = element_blank(),
                   panel.grid.major = element_blank(),
                   panel.grid.minor = element_blank(),
                   strip.background = element_rect(fill="white"))


### Knowledge Rating bar plot

Plot1<- ggplot(df.exp_long, aes(x=ignorance, y=know_rating, fill=ignorance)) + 
 coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(1, 7, by=1))+
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha=0.5) +
  stat_summary( fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.90), width = 0.2) +
  geom_jitter(position = position_jitterdodge(jitter.height = 0.2, dodge.width = 0.90, jitter.width=0.15), alpha = 
  0.3, colour="grey")+
    scale_fill_manual(values=c("lightyellow4", "gold"))+
  #scale_fill_brewer(palette="Dark2")+
  labs( y="Could have known Rating")+
  theme_bw()+
  myTheme

Plot1

### Blame Rating bar plot

Plot2 <- ggplot(df.exp_long, aes(x=ignorance, y=blame_rating, fill=ignorance)) + 
 coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(1, 7, by=1))+
  stat_summary(fun.y = mean, geom = "bar", position = "dodge", colour = "black", alpha=0.5) +
  stat_summary( fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.90), width = 0.2) +
  geom_jitter(position = position_jitterdodge(jitter.height = 0.2, dodge.width = 0.90, jitter.width=0.15), alpha = 
  0.3, colour="grey")+
    scale_fill_manual(values=c("ivory3", "khaki"))+
  #scale_fill_brewer(palette="Dark2")+
  labs( y="Blame for Ignorance Rating")+
  theme_bw()+
  myTheme

Plot2

### Causality - Knowledge Rating regression plot


Plot3<- ggplot(df.exp_long, aes(x=know_rating, y=causal_rating, fill=ignorance, colour= ignorance)) + 
 coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(1, 7, by=1))+
    scale_x_continuous(breaks = seq(1, 7, by=1))+
  stat_smooth(method = "lm", col = "black", fullrange=F,aes(fill=ignorance)) +
  #geom_jitter(position = position_jitterdodge(jitter.height = 0.2, dodge.width = 0.90, jitter.width=0.15), alpha = 
  #0.3, colour="grey")+
    scale_fill_manual(values=c("lightyellow4", "gold"))+
  #scale_fill_brewer(palette="Dark2")+
  labs( y="Causal Rating", x ="Could have known Rating")+
  theme_bw()+
  myTheme+
  theme(axis.title.x  = element_text(color="black", size = 14, vjust=.9))

Plot3

### Causality - Blame Rating regression plot


Plot4<- ggplot(df.exp_long, aes(x=know_rating, y=blame_rating, fill=ignorance, colour= ignorance)) + 
 coord_cartesian(ylim = c(1,7)) +
  scale_y_continuous(breaks = seq(1, 7, by=1))+
    scale_x_continuous(breaks = seq(1, 7, by=1))+
  stat_smooth(method = "lm", col = "black", fullrange=F,aes(fill=ignorance)) +
  #geom_jitter(position = position_jitterdodge(jitter.height = 0.2, dodge.width = 0.90, jitter.width=0.15), alpha = 
  #0.3, colour="grey")+
    scale_fill_manual(values=c("ivory3", "khaki"))+
  #scale_fill_brewer(palette="Dark2")+
  labs( y="Blame for Ignorance Rating", x = "Could have known Rating")+
  theme_bw()+
  myTheme+
  theme(axis.title.x  = element_text(color="black", size = 14, vjust=.9))

Plot4

### merge plots with `knowledge' and `no knowledge' condition
Fig3d <- ggarrange(Plot1, Plot2, Plot3, Plot4,
                    ncol = 2, 
                    nrow = 2)
### show plot
plot(Fig3d)

### save plot
ggsave(Fig3d, file="Fig3d.pdf", dpi=400, height = 8, width = 8)


```


